### 2016-09-30 intro.tex
no message

The concerns outlined above motivate a careful treatment of data
structures in an adversarial setting, where both \emph{soundness}
\jnote{I like ``soundness'' better than ``correctness,'' but I won't
insist.} and \emph{privacy} are considered. In this work we initiate
such a treatment for abstract data structures, and also explore the
security of several specific data structures---that can all be
viewed as generalizations of Bloom
filters~\cite{bloom1970space}---supporting (approximate)
set-membership queries. Specifically, we show \ldots \todo{highlight
that we are able surface ways in which constructions
  are sensitive to use cases, i.e. schemes secure with secret hash
  functions but not with public hash functions}
\todo{Somewhere in the intro, might what to face the ``nothing hard''
  criticism head on.  Perhaps mention that many of the results follow
  a common pattern (which, for privacy, we tease out in a general
  theorem), and that often the most technically difficult part is
  connnecting the adaptive setting to the zero-query setting.}

>>>>

The concerns outlined above motivate a careful treatment of data
structures in an adversarial setting, where both \emph{soundness}
and \emph{privacy} are considered. In this work we initiate such a
treatment for abstract data structures, and also explore the
security of several specific data structures---that can all be
viewed as generalizations of Bloom
filters~\cite{bloom1970space}---supporting (approximate)
set-membership queries. Specifically, we show \ldots \todo{highlight
that we are able surface ways in which constructions
  are sensitive to use cases, i.e. schemes secure with secret hash
  functions but not with public hash functions}
\todo{Somewhere in the intro, might what to face the ``nothing hard''
  criticism head on.  Perhaps mention that many of the results follow
  a common pattern (which, for privacy, we tease out in a general
  theorem), and that often the most technically difficult part is
  connnecting the adaptive setting to the zero-query setting.}

### 2016-09-30 notions.tex
no message

\fixme{Do we say that all notions can be extended to the ROM by giving
all all algorithms to a RO~$H$?  Is this true for the SS-privacy
notion?  (It seems to make sense elsewhere.)}

@@

\jnote{Entirely general, only specializing to set-membership data structures when needed.}

@@

\begin{theorem}
Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$ and
attacker~$A$, there is an attacker $A'$ running in about the same time with
\[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
%Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
%with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
%Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
\begin{theorem}\todo{rewrite}
Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
\end{theorem}
\begin{proof}
%Fix a  and an attacker
%$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
Define $A'$ as follows: first, it samples a set $S$ according to
distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
Finally, it outputs~1 if and only if $z \in S$.

It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
But for any simulator $\Sim$,
the only information
that $\Sim$
and $A'$ jointly have in the ideal world
about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \leq
2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
The theorem follows.
\end{proof}

@@

%\jnote{Not sure how general to make the above. Need to verify that it is general enough
%to prove security of all the constructions we care about.}
%\tsnote{Point out an example or two of the schemes this
%  covers.  Domain-separated PRF BF, for example.  I think it covers
%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
%  functions and does the hashing. (Although the following theorem does
%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
%  \jnote{I say we state the general theorem in Section~3.2 and just
%  promise that applications will come in Section~4.}
We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
of~$\Rep$. \hfill\dqed
\end{definition}
%\tsnote{Point out an example or two of the schemes this
%  covers.  Domain-separated PRF BF, for example.  I think it covers
%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
%  functions and does the hashing. (Although the following theorem does
%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
%  \jnote{I say we state the general theorem in Section~3.2 and just
%  promise that applications will come in Section~4.}\tsnote{Yes.}
We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
\jnote{Need notation for the advantage in the PRF experiment.}

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq

For ${\sf leak}(S) = |S|$,

If $F$ is a $(t, \epsilon)$-pseudorandom
function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
with respect to leakage function

.
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. In then computes: (1)~$s_1,
\ldots, s_t \getsr \Rep_1(S^*)$; (2)~$K \getsr \calK$; (3)~$\pubaux
\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
$\pubaux$.

>>>>

\fixme{Do we say that all notions can be extended to the ROM by giving
all all algorithms to a RO~$H$?  Is this true for the SS-privacy
notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}

@@

@@

\begin{theorem}
Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$ and
attacker~$A$, there is an attacker $A'$ running in about the same time with
\[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
%Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
%with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
%Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
\end{theorem}
\begin{proof}
%Fix a  and an attacker
%$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
Define $A'$ as follows: first, it samples a set $S$ according to
distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
Finally, it outputs~1 if and only if $z \in S$.

It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
But for any simulator $\Sim$,
the only information
that $\Sim$
and $A'$ jointly have in the ideal world
about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A', \Sim}=1} \leq
2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
The theorem follows.
\end{proof}

@@

%\jnote{Not sure how general to make the above. Need to verify that it is general enough
%to prove security of all the constructions we care about.}
%\tsnote{Point out an example or two of the schemes this
%  covers.  Domain-separated PRF BF, for example.  I think it covers
%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
%  functions and does the hashing. (Although the following theorem does
%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
%  \jnote{I say we state the general theorem in Section~3.2 and just
%  promise that applications will come in Section~4.}

We next show that any canonical data structure in which~$F$ is a pseudorandom function is
semantically secure with respect to leakage consisting of the size of the set.
\jnote{Need notation for the advantage in the PRF experiment.}

\begin{theorem}
Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
has canonical representation
$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
any attacker $A$, there is an attacker
$A'$ running in about the same time for which
\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
\end{theorem}
\begin{proof}
We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
\ldots, s_t \getsr \Rep_1(S^*)$, chooses a uniform key
$K \getsr \calK$, runs $\pubaux
\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
$\pubaux$.
